Sketch Recognition and Understanding

### 2009-08-10 trunk/draft/System.tex
after 11 august change

\subsection{Support Vector Machines}
\label{Sec:SVMdetail}
The foundation of Support Vector Machines (SVM) were developed by Vapnik \cite{} in 1995. It is gainig increase popularity due to the high performance and efficient implementation. The goal of SVM algorithms is to generate a sperating plane between two different classes which are represented using a set of n-dimentional vectors. The generated plane is used as a good classifier to the unseen exmaples. However, there can be more than one plane that can separates the data therefore SVM attempts to find the plane that maximize the margin (distance between classifier and nearest sample) between the two classes \ref{}. To calcuate the margin, two different hyperplanes are constructed, one plane on each side of the data, these two planes are then moved to generenate the maximum margin possilbe.

@@

 The vector $\omega$ determines th orientation of a seperation plane. The scalar $b$ determines the offeset of the plane from the orgin. Lets assume that the datatpointa re linearly seperable, i.e. there are infinitely many possible seperating planes that correctly classify the training data. Figure\ref{} illustrates two different seperating planes. It is intuitively noted from the figure that the () line is more likely to generalize more data and thus introduce less classification error. This can be geometrically characterized as plane furthest from both classes.     % Which one is preferable ? Intuitively one perfers the solid pane since small perturbations of any point would not introduce misclassifications errors. Without any information, the solid plane is more likely to generalize better on future data. Geometrically we can characterize the solid plane as being furthuret from both classes.

The SVM problem is how to construct the plane that is furthuest from both classes. One approcah is to maximize the margin between two parallel planes supporting. A plane supports a class if all points in that class are on one side of that plane. For the points with the class label $+1$ we would like there exist $\omega$ and $b$ such that $\omega \cdot x_i\> b$ or $\omega \cdot x_i -b \> 0$  depending on the class label. Let us suppose that smallest value of $\mid \omega \cdot x_i -b\mid$ iss $\kappa$, then when $ \omega \cdot x_i -b \geq \kappa$. The argument insidee the decision function is invariant under positive rescalling so we will implicity fix a scale by requiring $\omega \cdot x_i -b \geq 1 $. For the points with class label $-1$ we similary require $\omega \cdot x_i -b \leq -1 $. To find the plane furthest from both setss, we can simply maximize the distance or margin between the support planes for each class as illustrated in Figure \ref{}. The support planes are pussshed apart untill they bump inot small number of data points ( the support vecotrs ) for each class. The support vectors in Figure \ref{} are outlined in (),

@@

\subsubsection{Linearly Inseperable Case}
 So far we have assumed that the two datasets are linearly separable. Th this is not true, the startegy of constructing the plane that bisect the two closest points of the convex hulls will fail. As illustrated in Figure \ref{}, if the points are not linearly seperable the primal supporitng plane will fails. Since the QP task is not feasible for ethe linearly inseperable case , then we need to relax the constrains. Consider the linear inseperable problem in Figure\ref{}, Ideally we would like no points to be missclassified and no points to fall in the margin. But we must relax the constrain that insure that each point in on the approiate side of tis supporitng plane. Any point fallihng on the wrong side of tis supprting plane is considered to be an error. We want to maximize the margin and minimize the error.

@@

\subsubsection {Non linear function Using Kernels}
If we consider a classification problem that cannot be seperated using a linear space (See Figure \ref{} ). A quadratic or  cubic function will work better in some casses. A classific method of converting a linear classification algoirhtm inot a nonolinear classification algoorithm is to simply add addional attribute to the data that are nonlinear functions of the original data. Existing linar classification algorithms can be then applied to the expanded dataset feature space producing non linear functions in the original input space. To construct a quadratic disceriminant in a two dimensional vector space with attributes $r$ and $s$, simply map the original two dimensional input space $\left[r,s\right]$ to the five dimensional features space $\left[r,s,rs,r^2,s^2\right]$ and construct a linear discriminiant in that space. specifically, define : $\vartheta(x):R^2  \rightarrow R^5$ then 
\begin{equation}
\begin{array}{l}
	x=[r,s] \\
	\omega \cdot x=\omega_1 r+ \omega_2 s \\
	\downarrow \\
	\vartheta(x)=\left[r,s,rs,r^2,s^2\right] \\

	 \omega \cdot \vartheta(x)= \omega_1 r+ \omega_2 s + \omega_3 rs+ \omega_4 r^2+\omega_5 r^2 
\end{array}
\label{eq:kernel}
\end{equation}  
The resulting classification function, 
\begin{equation}
\begin{array}{l}
f(x)=sign\left( \omega \cdot\vartheta(x)-b \right) \\
= sign\left( \omega_1 r+ \omega_2 s + \omega_3 rs+ \omega_4 r^2+\omega_5 r^2 -b \right) 
\end{array}
\label{eq:kern2}
\end{equation}  
is linear in the mapped five dimensional feature space but is quadratic in the two dimensional input space.

@@

Exampine what happens when athe nonlinear mapping is introduced to equation \ref{eq:dual}. Let us define : $\vartheta(x):R^2\rightarrow R^5 \quad n>> n$  we need to optimize

>>>>

\subsection{Support Vector Machines}
\label{Sec:SVMdetail}
The foundation of Support Vector Machines (SVM) were developed by Vapnik \cite{svmintroduce} in 1995. It is gainig increase popularity due to the high performance and efficient implementation. The goal of SVM algorithms is to generate a sperating plane between two different classes which are represented using a set of n-dimentional vectors. The generated plane is used as a good classifier to the unseen exmaples. However, there can be more than one plane that can separates the data therefore SVM attempts to find the plane that maximize the margin (distance between classifier and nearest sample) between the two classes \ref{fig:svm1}. To calcuate the margin, two different hyperplanes are constructed, one plane on each side of the data, these two planes are then moved to generenate the maximum margin possilbe.  
\begin{figure}
	\centering
		\includegraphics{afterDefense/svm1.jpg.eps}
	\caption{Different Classifier planes }
	\label{fig:svm1}
\end{figure}

@@

 The vector $\omega$ determines th orientation of a seperation plane. The scalar $b$ determines the offeset of the plane from the orgin. Lets assume that the datatpointa re linearly seperable, i.e. there are infinitely many possible seperating planes that correctly classify the training data. Figure\ref{fig:svm1} illustrates two different seperating planes. It is intuitively noted from the figure that the solid line is more likely to generalize more data and thus introduce less classification error. This can be geometrically characterized as plane furthest from both classes.     % Which one is preferable ? Intuitively one perfers the solid pane since small perturbations of any point would not introduce misclassifications errors. Without any information, the solid plane is more likely to generalize better on future data. Geometrically we can characterize the solid plane as being furthuret from both classes.

The SVM problem is how to construct the plane that is furthuest from both classes. One approcah is to maximize the margin between two parallel planes supporting. A plane supports a class if all points in that class are on one side of that plane. For the points with the class label $+1$ we would like there exist $\omega$ and $b$ such that $\omega \cdot x_i\> b$ or $\omega \cdot x_i -b \> 0$  depending on the class label. Let us suppose that smallest value of $\mid \omega \cdot x_i -b\mid$ iss $\kappa$, then when $ \omega \cdot x_i -b \geq \kappa$. The argument insidee the decision function is invariant under positive rescalling so we will implicity fix a scale by requiring $\omega \cdot x_i -b \geq 1 $. For the points with class label $-1$ we similary require $\omega \cdot x_i -b \leq -1 $. To find the plane furthest from both setss, we can simply maximize the distance or margin between the support planes for each class as illustrated in Figure \ref{fig:svm2}. The support planes are pussshed apart untill they bump inot small number of data points ( the support vecotrs ) for each class. The support vectors in Figure \ref{fig:svm2} are filled datapoints , 
\begin{figure}
	\centering
		\includegraphics{afterDefense/svm2.jpg.eps}
	\caption{Margin of Support planes }
	\label{fig:svm2}
\end{figure}

@@

\subsubsection{Linearly Inseperable Case}
 So far we have assumed that the two datasets are linearly separable. Th this is not true, the startegy of constructing the plane that bisect the two closest points of the convex hulls will fail. As illustrated in Figure \ref{fig:svm5}, if the points are not linearly seperable the primal supporitng plane will fails. Since the QP task is not feasible for ethe linearly inseperable case , then we need to relax the constrains. Consider the linear inseperable problem in Figure\ref{fig:svm5}, Ideally we would like no points to be missclassified and no points to fall in the margin. But we must relax the constrain that insure that each point in on the approiate side of tis supporitng plane. Any point fallihng on the wrong side of tis supprting plane is considered to be an error. We want to maximize the margin and minimize the error.

\begin{figure}
	\centering
		\includegraphics{afterDefense/svm5.jpg.eps}
	\caption{Linearly Inseperable}
	\label{fig:svm5}
\end{figure}

@@

\subsubsection {Non linear function Using Kernels}
If we consider a classification problem that cannot be seperated using a linear space (See Figure \ref{fig:svm6} ). A quadratic or  cubic function will work better in some casses. A classific method of converting a linear classification algoirhtm inot a nonolinear classification algoorithm is to simply add addional attribute to the data that are nonlinear functions of the original data. Existing linar classification algorithms can be then applied to the expanded dataset feature space producing non linear functions in the original input space. To construct a quadratic disceriminant in a two dimensional vector space with attributes $r$ and $s$, simply map the original two dimensional input space $\left[r,s\right]$ to the five dimensional features space $\left[r,s,rs,r^2,s^2\right]$ and construct a linear discriminiant in that space. specifically, define : $\vartheta(x):R^2  \rightarrow R^5$ then 
\begin{equation}
\begin{array}{l}
	x=[r,s] \\
	\omega \cdot x=\omega_1 r+ \omega_2 s \\
	\downarrow \\
	\vartheta(x)=\left[r,s,rs,r^2,s^2\right] \\

	 \omega \cdot \vartheta(x)= \omega_1 r+ \omega_2 s + \omega_3 rs+ \omega_4 r^2+\omega_5 r^2 
\end{array}
\label{eq:kernel}
\end{equation}

The resulting classification function, 
\begin{equation}
\begin{array}{l}
f(x)=sign\left( \omega \cdot\vartheta(x)-b \right) \\
= sign\left( \omega_1 r+ \omega_2 s + \omega_3 rs+ \omega_4 r^2+\omega_5 r^2 -b \right) 
\end{array}
\label{eq:kern2}
\end{equation}  
is linear in the mapped five dimensional feature space but is quadratic in the two dimensional input space.

\begin{figure}
	\centering
		\includegraphics{afterDefense/svm6.jpg.eps}
	\caption{non Lineary problem }
	\label{fig:svm6}
\end{figure}

@@

Examine what happens when athe nonlinear mapping is introduced to equation \ref{eq:dual}. Let us define : $\vartheta(x):R^2\rightarrow R^5 \quad n>> n$  we need to optimize
